---
title: "Beyond the Stage"
author: "Margaret Sun"
date: "4/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Import relevant libraries

library(tidyverse)
library(tidytext)
library(ggplot2)
```

## Final Project Milestone


<br/>

#### Question:

Twitter API portions to come: if we are not looking at Python ever again in class, am I allowed to use it for the Final Project? 

<br/>

#### Data Description: 

* Data included thus far represents the fundamental organization of the project, by tour dates and locations for the band BTS' world tour, "BTS World Tour: Love Yourself". 

* "love_yourself" includes all dates, geographic locations, attendance, and revenue of each concert stop

* Attendance and revenue for the following shows were found as the sum of all shows at the respective location: Seoul, North American cities, London, Berlin, Paris, Japan cities,  Taoyuan, Hong Kong, Bangkok

* Data for each show is the sum divided by the number of shows per city, and may differ from actual venues, consider redividing in proportion to relative stadium capacities

* While the source is the summary chart for the Wikipedia page for "BTS World Tour: Love Yourself", each of the numbers in the chart links to local coverage of concert sales, pulling from numerous news sources

<br/>

#### Sample Graphic

```{r download, echo=FALSE, message=FALSE, warning=FALSE}

# Read in data set

love_yourself <- read_csv("love_yourself.csv")
```

```{r graphic, echo=FALSE}

love_yourself %>% 
  select(city, continent, attendance) %>% 
  group_by(city, continent) %>% 
  count(attendance) %>% 

  ggplot(aes(x = city, y = attendance, color = continent)) +
  geom_col() +
  coord_flip() +
  labs(title = "Average Attendance of Each Concert Stop",
       subtitle = "BTS World Tour: Love Yourself",
       caption = "Source: Wikipedia chronology compiled from news articles") +
  xlab("City") +
  ylab("Attendance")

```